Resource Buying Games

### 2017-04-02 paper.tex
theorem non-matroid strategy space

\section{Non-Matroid Strategy Spaces}
Finally, we consider in this section non-matroid strategy spaces. Specifically,
we present a construction which illustrates how to obtain a weighted two player
resource buying game with marginally non-increasing cost functions which does
not posses a PNE starting from a non-matroid anti-chain $S$. This implies that
matroids are exactly the structures to consider using marginally non-increasing
cost functions since other structures cannot guarantee the existence of PNEs.

>>>>

\section{Non-Matroid Strategy Spaces}
Finally, we consider in this section non-matroid strategy spaces. Specifically,
we present a construction which illustrates how to obtain a weighted two player
resource buying game with marginally non-increasing cost functions which does
not posses a PNE starting from a non-matroid anti-chain $S$. This implies that
matroids are exactly the structures to consider using marginally non-increasing
cost functions since other structures cannot guarantee the existence of PNEs.
Thus, we prove the following theorem:
\begin{theo}
  For every non-matroid anti-chain $\mathcal{S}$ on a set of resources $E$,
  there exists a weighted two-player resource buying game
  $G = \tupel{\tilde{E},
    (\mathcal{S}_{1}\times \mathcal{S}_{2})\times\mathcal{P},\pi}$
  having marginally non-increasing cost functions, whose strategy spaces
  $\mathcal{S}_{1}$ and $\mathcal{S}_{2}$ are both isomorphic to $\mathcal{S}$,
  so that $G$ does not posses a PNE.
\end{theo}
